dyngen: a multi-modal simulator for spearheading new single-cell omics analyses

### 2021-05-17 manuscript/supplementary_files.Rmd
update

data("realcounts", package = "dyngen")
name_realcounts <- "zenodo_1443566_real_silver_bone-marrow-mesenchyme-erythrocyte-differentiation_mca"
url_realcounts <- realcounts %>% filter(name == name_realcounts) %>% pull(url)
realcount <- dyngen:::.download_cacheable_file(url_realcounts, getOption("dyngen_download_cache_dir"), verbose = FALSE)
```

@@

ggplot(timings1) + 
  geom_bar(aes(x = forcats::fct_inorder(as.character(num_cells)), y = time_elapsed, fill = forcats::fct_inorder(group)), stat = "identity") +
  theme_classic() +
  scale_fill_brewer(palette = "Dark2") +
  labs(x = "Number of cells", y = "Average time (s)", fill = "dyngen step")
```

@@

ggplot(timings2) + 
  geom_bar(aes(x = forcats::fct_inorder(as.character(num_features)), y = time_elapsed, fill = forcats::fct_inorder(group)), stat = "identity") +
  theme_classic() +
  scale_fill_brewer(palette = "Dark2") +
  labs(x = "Number of features", y = "Average time (s)", fill = "dyngen step")
```

>>>>

data("realcounts", package = "dyngen")
name_realcounts <- paste0(
  "zenodo_1443566_real_silver_", 
  "bone-marrow-mesenchyme-erythrocyte-differentiation_mca"
)
url_realcounts <- realcounts %>% filter(name == name_realcounts) %>% pull(url)
cache_dir <- getOption("dyngen_download_cache_dir")
realcount <- 
  dyngen:::.download_cacheable_file(url_realcounts, cache_dir, verbose = FALSE)
```

@@

ggplot(timings1) + 
  geom_bar(aes(
    x = forcats::fct_inorder(as.character(num_cells)), 
    y = time_elapsed,
    fill = forcats::fct_inorder(group)),
    stat = "identity") +
  theme_classic() +
  scale_fill_brewer(palette = "Dark2") +
  labs(x = "Number of cells", y = "Average time (s)", fill = "dyngen step")
```

@@

ggplot(timings2) + 
  geom_bar(aes(
    x = forcats::fct_inorder(as.character(num_features)), 
    y = time_elapsed, 
    fill = forcats::fct_inorder(group)),
    stat = "identity") +
  theme_classic() +
  scale_fill_brewer(palette = "Dark2") +
  labs(x = "Number of features", y = "Average time (s)", fill = "dyngen step")
```
